Make any stupid plot you want

### 2020-11-12 draft/sections/math.tex
mostly notes from yesterday

| Fiber Bundle | Spivak |
|--------------|--------|
| B | K |
| F | U |
| embedded in F  | (C, \sigma), \pi |
| E/V |  |
|   | \tau:  K-\Gamma(sigma) |
|   |

@@

\subsubsection{Data}
We use Butler's visualization model built on the mathematics of fiber bundles \cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989} and Spivak's schema like description of fibers \cite{spivakSIMPLICIALDATABASES} as the basis of our data model.  The components of the fiber bundle are:
\begin{definition}
    \item[$K$] base space that describes the topology of the data, is the indexer in data contain
\end{definition}

\begin{center}
    \begin{tabular}{ c c c }
     term & mathematical definition & data container analogue\\
      $K$ & base space along which the data lies & indexer \\
      $F$ & fiber space from which possible values are pulled & schema \\
      $E$ & trivial: $F= K \times F$, non-trivial \dots &

    \end{tabular}
\end{center}

\begin{equation}

\end{equation}

\subsection{artist}
%%category theory diagrams to show artist is a functor, which is how you get invariance
%% artist is parameterized on taus
%% artists are curried collection of taus , orbits of artists are the visual idiomsW
\begin{equation}
    A: \Gamma(V), \Taus \mapsto f:\T \mapsto R^{7}
\end{equation}

%%%in practuce this has currently same topology as gamma V
\begin{equation}%%pull in spivak
    \tau: one type in the fiber \mapsto different type in the T fiber 
\begin{equation}

>>>>

@@

\subsubsection{Data}
We use Butler's visualization model built on the mathematics of fiber bundles \cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989} and Spivak's schema like description of fibers \cite{spivakSIMPLICIALDATABASES} as the basis of our data model.  The components of the fiber bundle are:

\begin{center}
    \begin{tabular}{ c c c }
     term & mathematical definition & data container analog\\
      $K$ & base space along which the data lies & indexer \\
      $F$ & fiber space from which possible values are pulled & schema \\
      $E$ & trivial: $F= K \times F$, non-trivial \dots & 
    \end{tabular}
\end{center}

trivial: 
locally trivial: take small enough regions, it becomes trivial, cutting it up into simplixes is one way to do so...
gluing maps are transition functions <- interesting things are in transition functions <- currently writing about pieces, they would write transition function validators and sections that we would check against
sheaf: association of u (point on eaerth) w/ its section (sheafs associates queries of data fibers over particular u)
pre-sheaf - just need space of sections for u
sheaf - if on section of u and section of v and they agree on intersection than their should be a section of union

\subsection{artist}
%%category theory diagrams to show artist is a functor, which is how you get invariance
%% artist is parameterized on taus
%% artists are curried collection of taus , orbits of artists are the visual idiomsW
\begin{equation}
    A: \sigma \in \Gamma(V), \Taus \mapsto f:\T \mapsto R^{7}
\end{equation}
$\sigma$ evaluated on $k \in K$
%%%in practuce this has currently same topology as gamma V
\begin{equation}%%pull in spivak
    \tau: one type in the fiber \mapsto different type in the T fiber
